---
title: "R Notebook"
output:
  word_document: default
  html_notebook: default
---

# Condorcet's jury formula

This notebook is a simple example of how to compute the formula in [Condorcet's jury theorem](http://www.statisticalconsultants.co.nz/blog/condorcets-jury-theorem.html) in R. First we define the method. We will use the formula, defined [here](http://demonstrations.wolfram.com/TheoreticalModelCondorcetsJuryTheoremPart1/):

$$
\sum_{k=\lceil N/2\rceil}^N {N \choose k} p^k(1-p)^{N-k}
$$

The `condorcet` method implements exactly the above formula
```{r}
condorcet <- function(N, p){
  k <- ceiling(N/2)  
  return(sum(sapply(k:N, function(k) choose(N, k) * p^k * (1-p)^(N-k))))
}

```


And now our sample data

```{r}
# generate a sequence from 5 to 100 by 10
N <- seq(5, 100, 10)
# the probabilities that the jury is right, we examine two different values of p
p <- c(0.6, 0.7)

# repeat the same data for two different probability sets
data <- rbind(N,N)
row.names(data) <- c("p=0.6", "p=0.7")
colnames(data) <- N
data
```

We apply the method to our data and the result we get are the following

```{r kable}
results <- data
# First row for p=0.6
results[1,] <- sapply(results[1,], function(x) condorcet(x, 0.6))
# Second row for p=0.7
results[2,] <- sapply(results[2,], function(x) condorcet(x, 0.7))
knitr::kable(results)
```

So even with 25 juries and 70% probability of them being correct, they have _98,3% probability of being the majority_.
